QPLIB: A Library of Quadratic Programming Instances

### 2016-07-29 QPLIB-2.2.tex
changed SDP to PSD

The ordering of the values in the previous lists is not irrelevant; in general, problems become ``harder'' when going from left to right. More specifically, for the \textit{F} and \textit{C} fields the order is that of \emph{strict} containment between problem classes: for instance, Linear objective functions are strictly contained in Diagonal convex quadratic ones (by just allowing the diagonal elements to be all-zero), which are strictly contained into general Convex quadratic ones (by allowing the off-diagonal elements to be all-zero), which in turn are strictly contained into general nonconvex Quadratic ones (by allowing any symmetric $Q^0$, hence possibly SDP ones as well). The only field for which the containment relationship is not a total order is \textit{V}, for which only the partial orderings
\[
 \mbox{C} \subset \mbox{M} \subset \mbox{G}
 \qquad,\qquad
 \mbox{B} \subset \mbox{M} \subset \mbox{G}
 \qquad,\qquad
 \mbox{B} \subset \mbox{I} \subset \mbox{G}
\]
hold. In the following discussion we will repeatedly exploit this by assuming that, unless otherwise mentioned, when a method can be applied to a given problem, it can be applied as well to all simpler problems where the value of each field is arbitrarily replaced with a value denoting a less-general class.

@@

When a $Q^i$ is positive semidefinite (SDP), i.e., the corresponding constraint/objective function is convex, general quadratic constraints are in fact equivalent to diagonal ones. In fact, every SDP matrix can be factorized as $Q^i = L^i (L^i)^\top$, e.g.~by the (incomplete) Cholesky factorization, $f^i(x) = x^\top Q^i x = \sum_{j \in \Mcn} z^2_jz$ where $z = x^\top L^i$. Hence, one could think that D** problems need not be distinguished from C** ones; however, this is true only for ``complicated'' constraints, but not for ``simple'' ones, because the above reformulation technique introduces linear constraints. Indeed, while C*L (and, a fortiori, C*\{C,Q\}) can always be brought to D*L (D*\{C,Q\}), using the same technique C*B becomes D*L, which is significantly different from D*B. In practice, a diagonal convex objective function under linear constraints is found in many applications ({\bf citations?}), so that D*L still makes sense to distinguish the case where the objective function is ``naturally'' separable from that where separability is artificially introduced, although this is in theory always possible.

>>>>

The ordering of the values in the previous lists is not irrelevant; in general, problems become ``harder'' when going from left to right. More specifically, for the \textit{F} and \textit{C} fields the order is that of \emph{strict} containment between problem classes: for instance, Linear objective functions are strictly contained in Diagonal convex quadratic ones (by just allowing the diagonal elements to be all-zero), which are strictly contained into general Convex quadratic ones (by allowing the off-diagonal elements to be all-zero), which in turn are strictly contained into general nonconvex Quadratic ones (by allowing any symmetric $Q^0$, hence possibly positive semidefinite ones as well). The only field for which the containment relationship is not a total order is \textit{V}, for which only the partial orderings
\[
 \mbox{C} \subset \mbox{M} \subset \mbox{G}
 \qquad,\qquad
 \mbox{B} \subset \mbox{M} \subset \mbox{G}
 \qquad,\qquad
 \mbox{B} \subset \mbox{I} \subset \mbox{G}
\]
hold. In the following discussion we will repeatedly exploit this by assuming that, unless otherwise mentioned, when a method can be applied to a given problem, it can be applied as well to all simpler problems where the value of each field is arbitrarily replaced with a value denoting a less-general class.

@@

When a $Q^i$ is positive semidefinite (PSD), i.e., the corresponding constraint/objective function is convex, general quadratic constraints are in fact equivalent to diagonal ones. In fact, every PSD matrix can be factorized as $Q^i = L^i (L^i)^\top$, e.g.~by the (incomplete) Cholesky factorization, $f^i(x) = x^\top Q^i x = \sum_{j \in \Mcn} z^2_jz$ where $z = x^\top L^i$. Hence, one could think that D** problems need not be distinguished from C** ones; however, this is true only for ``complicated'' constraints, but not for ``simple'' ones, because the above reformulation technique introduces linear constraints. Indeed, while C*L (and, a fortiori, C*\{C,Q\}) can always be brought to D*L (D*\{C,Q\}), using the same technique C*B becomes D*L, which is significantly different from D*B. In practice, a diagonal convex objective function under linear constraints is found in many applications ({\bf citations?}), so that D*L still makes sense to distinguish the case where the objective function is ``naturally'' separable from that where separability is artificially introduced, although this is in theory always possible.
